\Huge ACM and Climate Change

### 2019-05-28 main.tex
Tidy more

\begin{figure}[t]
\centering
\includegraphics[width=4in]{wmo_stripes.png}
\caption{Variation in annual global temperature, 1850 to 2018 (range from
  blue to red: $1.35^\circ$C) \cite{WarmingStripes}}
\label{fig:warming}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=2in]{IPCC-cover.png}
\caption{2018 IPCC report \cite{IPCC18}.  Key finding: Emissions must
  decline by at least 40 percent by 2030 and reach net zero by 2050, if we
  are to hold warming to 1.5 degrees.  There is ``no documented historic
  precedent'' for the transformation of the world economy needed to achieve
  this.  }
\label{fig:IPCC-cover}
\end{figure}

@@

A broad scientific consensus warns that the earth is warming, due to human
emissions of carbon dioxide and other greenhouse gases (Figure
\ref{fig:warming}). This is not a problem we can leave to future
generations: we are up against it now. The UN's Intergovernmental
Panel on Climate Change (IPCC) recently recommended a 40\% decrease in
emissions by 2030 to avoid irreversible damage
(Figure~\ref{fig:IPCC-cover}). Achieving reductions on this scale will
require urgent and sustained commitment at all levels of society, including
non-governmental organizations such as universities, companies, and scientific
societies like ACM.

>>>>

% \begin{figure}[t]
% \centering
% \includegraphics[width=4in]{wmo_stripes.png}
% \caption{Variation in annual global temperature, 1850 to 2018 (range from
%   blue to red: $1.35^\circ$C) \cite{WarmingStripes}}
% \label{fig:warming}
% \end{figure}

% \begin{figure}[t]
% \centering
% \includegraphics[width=2in]{IPCC-cover.png}
% \caption{2018 IPCC report \cite{IPCC18}.  Key finding: Emissions must
%   decline by at least 40 percent by 2030 and reach net zero by 2050, if we
%   are to hold warming to 1.5 degrees.  There is ``no documented historic
%   precedent'' for the transformation of the world economy needed to achieve
%   this.  }
% \label{fig:IPCC-cover}
% \end{figure}

@@

A broad scientific consensus warns that the earth is warming, due to human
emissions of carbon dioxide and other greenhouse gases.
% (Figure \ref{fig:warming}).
This is not a problem we can leave to future
generations: we are up against it now. The UN's Intergovernmental
Panel on Climate Change (IPCC) recently recommended a 40\% decrease in
emissions by 2030 to avoid irreversible damage~\cite{IPCC-report}.
% (Figure~\ref{fig:IPCC-cover}).
Achieving reductions on this scale will
require urgent and sustained commitment at all levels of society, including
non-governmental organizations such as universities, companies, and scientific
societies like ACM.
